Using best practices for forecasting biodiversity changes in breeding birds

### 2017-07-28 manuscript/draft.Rmd
add example to sum up this paragraph
also remove note to check Petchey et al. They do not make this
statement about different models, their discussion of the this
is mostly about modeling at different grains

For the error metric that evaluates both models' point estimates and their
uncertainty simultaneously, the JSDM and the nonlinear richness model converge
towards the time-series baselines at the longest time-scales assessed. This
convergence at longer time scales highlights the importance of considering how
forecasting method performance changes with the distance into the future being
predicted (Box 1). The value of this approach, and associated forecast horizons,
has been raised for knowing how far into the future a model can be effectively
used for forecasting [@petchey2015], but our results suggest a broader value to
this approach for considering the potential importance of different models and
processes for making forecasts at different scales. [[Should make sure Petchey et
al. don't make this point]] Our results show that for forecasts 1-3 years in the
future, baselines and time-series based approaches outperform all other methods
using integrative metrics. At these time scales, environmental changes are
relatively small and changes in the biota may lag behind changes in the
environment. However, as the timescale of the forecast increases to a decade the
JSDMs and environmental richness models get closer to the accuracy of the
time-series methods and even surpass some of those methods. As the forecast
distance increases the amount of environmental change is expected to increase
and the system will have more time to respond, potentially leading to shifts
towards improved relative performance of the models incorporating environmental
and ecological information. If this shift with forecast distance in the relative
importance of different processes and models continues, this could lead to JSDMs
and environmental richness models outperforming time-series based approaches at
sufficiently long time scales. These results suggest that assessment of how
forecast performance changes with time lag is not only important for determining
how far in the future to forecast, but also for determining models and processes
are most relevant for making forecasts at different time scales.

>>>>

For the error metric that evaluates both models' point estimates and their
uncertainty simultaneously, the JSDM and the nonlinear richness model converge
towards the time-series baselines at the longest time-scales assessed. This
convergence at longer time scales highlights the importance of considering how
forecasting method performance changes with the distance into the future being
predicted (Box 1). The value of this approach, and associated forecast horizons,
has been raised for knowing how far into the future a model can be effectively
used for forecasting [@petchey2015], but our results suggest a broader value to
this approach for considering the potential importance of different models and
processes for making forecasts at different scales. Our results show that for
forecasts 1-3 years in the future, baselines and time-series based approaches
outperform all other methods using integrative metrics. At these time scales,
environmental changes are relatively small and changes in the biota may lag
behind changes in the environment. However, as the timescale of the forecast
increases to a decade the JSDMs and environmental richness models get closer
to the accuracy of the time-series methods and even surpass some of those
methods. As the forecast distance increases the amount of environmental change
is expected to increase and the system will have more time to respond,
potentially leading to shifts towards improved relative performance of the
models incorporating environmental and ecological information. If this shift
with forecast distance in the relative importance of different processes and
models continues, this could lead to JSDMs and environmental richness models
outperforming time-series based approaches at sufficiently long time scales.
These results suggest that assessment of how forecast performance changes with
time lag is not only important for determining how far in the future to
forecast, but also for determining which models and processes are most relevant
for making forecasts at different time scales. For example ensemble forecasts
could be created which incorporate these time lags into the weights for
individual models.
